---
title: "Neural Progenitor Cells for Treatment of Spinal Cord Injury"
output: html_document
---

# *Gene expression of pro-inflammatory cytokines/chemokines*

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
#1. INSTALLING PACKAGES
#install.packages("ggplot2")
#install.packages("data.table")
#install.packages("RColorBrewer")
#install.packages("cowplot")
#install.packages("gridExtra")
#install.packages("gplots")

#2. ATTACHING PACKAGES
library(ggplot2)
library(data.table)
library(RColorBrewer)
library(cowplot)
library(knitr)
library(gridExtra)
library(grid)
library(gplots)

rm(list=ls())

#Importing function for sharing legend 
source("/home/ramhak/Dropbox/PHD/PAPER I/R_v2/Function_directory/get_legend.R")

```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
################################################################## DATA MANIPULATION ############################################################
```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
#1. IMPORTING DATA
DT_raw <- fread("RTqPCR_raw_data.csv")
DT <-  DT_raw
#2. REMOVING UNNECESSARY COLUMNS
DT[, c("Ctrl", "Expression SEM", "Corrected Expression SEM", "Mean Cq", "Cq SEM"):=NULL]
#3. ADJUSTING SAMPLE COLUMN
DT[, Animal:=substr(Sample, nchar(Sample), nchar(Sample))] #adding column -> allows for summary per animal later on
DT[, Sample:=substr(Sample, 1, nchar(Sample)-1)] #cleaning sample column
DT[Sample=="Control", Sample:="saline"] #renamning
DT[Sample=="no_injury", Sample:="healthy"] #reanaming
#4. ADJUSTING TARGET COLUMN
DT <- DT[!(Target%in%c("Actin_V1", "Actin_v1", "GAPDH_v3", "HPRT_red"))] #removing reference genes
DT[Target=="Il1b", Target:="IL1b"]
DT[Target=="GM_CSF", Target:="GM-CSF"]
DT <- DT[!(Target=="CCL3")] #two targets for CCL3/MIP1a accidentally included. Removing CCL3.
#5. ADJUSTING EXPRESSION COLUMNS
DT[,Expression:=as.numeric(gsub(",", ".", Expression))]

```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
#1. NORMALISATIOON OF EXPRESSION VALUES TO HEALTHY
expression_normalizer <-  function(list_object){
  divisor <-  list_object[Sample=="healthy", ifelse(mean(Expression)==0, 1, mean(Expression))]
  list_object[,Expression:=ifelse(Expression==0, 1, Expression)]
  #Function normalizes the expression data to the mean of healthy animals. norm_value = over/under expression in %
  normalizer <- function(one_value){
       if(one_value>0 & divisor>0){return(one_value/divisor)}
       if(one_value>0 & divisor<0){return((one_value-divisor)/(-1*divisor))}
       if(one_value<0 & divisor>0){return(1/((divisor-one_value)/divisor))}
       if(one_value<0 & divisor<0){return(1/(one_value/divisor))}
   }

   norm_value_col <- data.table(do.call(rbind, lapply(list_object[, Expression], function(val){normalizer(val)})))
   list_object[, "Expression_normalized"] <- log2(norm_value_col)
  return(list_object)
}

DT <- do.call(rbind, lapply(split(DT, DT[ ,Target]), function(object){expression_normalizer(object)}))
```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
#1. MEAN LEVEL OF PRO-INFLAMMATION IN EACH ANIMAL 
DT_animal <- DT[Sample!="healthy", .(Expression_normalized=mean(Expression_normalized)), by=c("Week","Sample", "Animal")]
#2. MEAN LEVEL OF PRO-INFLAMMATION IN EACH TREATMENT AT EACH TIME POINT
DT_summary <- DT[Sample!="healthy", .(Expression_normalized=mean(Expression_normalized)), by=c("Week","Sample", "Animal")][, .(Expression_normalized=mean(Expression_normalized), sd=sd(Expression_normalized), n=.N), by=c("Week", "Sample")]
DT_summary <- DT_summary[, SEMx1.96:=qnorm(0.975)*sd/sqrt(n)][, `:=`(CI.lower=Expression_normalized-SEMx1.96, CI.upper=Expression_normalized+SEMx1.96)]
```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
################################################################## INFLAMMATION ############################################################
```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
#1. INTRADAY P-VALUES
inflammation_intraday_p_value <- function(list_object){
  calc_data <- list_object
  #Evaluating assumptions
  norm_p_value <- do.call(rbind, lapply(split(calc_data, calc_data[, .(Sample)]), function(subset){data.table(Sample=subset$Sample, p_value=shapiro.test(subset$Expression_normalized)$p.value)}))
  norm_p_value <- norm_p_value[, .(p_value=mean(p_value)), by="Sample"]
  
  homo_p_value <-  fligner.test(calc_data[,Expression_normalized], calc_data[,factor(Sample)])$p.value

  if(isTRUE(norm_p_value[Sample=="NPC", p_value]>0.05)&isTRUE(norm_p_value[Sample=="saline", p_value]>0.05)){
    if(homo_p_value>0.05){
      p_value <- t.test(calc_data[Sample=="NPC", Expression_normalized], calc_data[Sample=="saline", Expression_normalized], var.equal = TRUE)$p.value
    } else {
      p_value <- t.test(calc_data[Sample=="NPC", Expression_normalized], calc_data[Sample=="saline", Expression_normalized], var.equal = FALSE)$p.value
    }
  } else {
    p_value <- wilcox.test(calc_data[Sample=="NPC", Expression_normalized], calc_data[Sample=="saline", Expression_normalized])$p.value
  }
  return(data.table(Week = calc_data[, Week][1], p_value = p_value))
}

inflammation_p_values <- do.call(rbind, lapply(split(DT_animal, DT_animal[,.(Week)]), function(subset){inflammation_intraday_p_value(subset)}))

```


```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
#1. ANALYSIS OF CHANGE IN EXPRESSION WITHIN TARGET AND TREATMENT OVER TIME
overtime_comparison_function <-  function(list_object, return_var){
  norm_p_values <- do.call(rbind, lapply(split(list_object, list_object[,.(Week)]), function(subset){
    if(nrow(subset)>2){p_value <- shapiro.test(subset$Expression_normalized)$p.value} else {p_value=0}
    return(p_value)}))
  
  homo_p_value <- fligner.test(list_object$Expression_normalized, list_object$Week)$p.value 
  
  if(all(norm_p_values>0.05)){
      if(homo_p_value>0.05){
      aov_raw <-  aov(Expression_normalized ~ factor(Week), data = list_object)
      p_value <- summary(aov_raw)[[1]]$`Pr(>F)`[1]
    } else { 
      aov_raw <- oneway.test(Expression_normalized ~ factor(Week), var.equal = FALSE, data = list_object)
      p_value <- as.numeric(aov_raw[3])
    }
    } else {
      aov_raw <-  aov(Expression_normalized ~ factor(Week), data = list_object)
      p_value <- summary(aov_raw)[[1]]$`Pr(>F)`[1]
    }
  
  if(return_var=="multiple_group_p"){return(data.table(treatment=list_object[, Sample][1], p_value = p_value))}
  if(return_var=="aov_object"){return(aov_raw)}

}

overtime_comparison_p <- do.call(rbind, lapply(split(DT_animal, DT_animal[,.(Sample)]), function(subset){overtime_comparison_function(subset, "multiple_group_p")}))

```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
#TIME OVERVIEW PLOT
timeoverview_plot <- ggplot(DT_summary, aes(x=Week, y=Expression_normalized, color=factor(Sample)))+
    geom_segment(aes(x=0.5, xend=12, y=0, yend=0), color="black", size=1, linetype=2)+
    annotate(geom="text", x=0, y=0, label="Healthy", fontface=2, size=4)+
    #Inflammation
    geom_errorbar(aes(ymin=CI.lower, ymax=CI.upper), position = position_dodge(width=1), size=3, width=1, show.legend = FALSE, alpha=0.6)+
    geom_point(shape=15, size=4, position = position_dodge(width=1))+
    geom_jitter(DT_animal, mapping=aes(x=Week, y=Expression_normalized, color=factor(Sample)), shape=18, size=3, position = position_jitterdodge(jitter.width = 0.5, dodge.width = 1), alpha=0.9)+
    geom_smooth(DT_animal, mapping=aes(x=Week, y=Expression_normalized, fill=factor(Sample)), se=TRUE, alpha=0.2, show.legend = FALSE)+
    #Targets
    geom_jitter(DT[Sample!="healthy"], mapping=aes(Week, y=Expression_normalized, color=factor(Sample)), size=1, position = position_jitterdodge(jitter.width = 1, dodge.width = 1), alpha=0.5)+    
    #Legends and shapes    
    xlab("Weeks (Post SCI)")+
    ylab("log2(fold change)")+
    scale_x_continuous(breaks=seq(0,12,1), limits=c(0,13)) +
   scale_y_continuous(breaks=seq(-7, 3, 1), limits = c(-7, 4))+
    theme(axis.title = element_text(size=20, face="bold"), legend.position = "bottom", legend.justification = "center", legend.text = element_text(size=18), legend.title = element_blank(), axis.text = element_text(size=16), axis.line.y = element_blank())+
    scale_color_manual(values=c(brewer.pal(3, "Set1")), name="Treatment:", labels=c("SCI+NPC (n=3 or 4/week)", "SCI+Saline (n=3 or 4/week)"))+
    scale_fill_manual(values=c(brewer.pal(3, "Set1")), name="Treatment:", labels=c("SCI+NPC (n=4 or 5/week)", "SCI+Saline (n=4 or 5/week)"))+
    #Annotations
    annotate(geom="text", label="UP-REGULATION", x=6.5, y=4, fontface=2, alpha=0.3, size=6)+
    annotate(geom="text", label="DOWN-REGULATION", x=6.5, y=-7, fontface=2, alpha=0.3, size=6)+
    #more annotations
    annotate(geom="text", x=0, y=2.8, label="SCI", fontface=2, size=5)+
    annotate(geom="text", x=1, y=2.8, label="NPC/\nSaline", fontface=2, size=4.5)+
    annotate(geom="text", x=2, y=2.8, label="2w", fontface=2, size=5)+
    annotate(geom="text", x=5, y=2.8, label="5w", fontface=2, size=5)+
    annotate(geom="text", x=12, y=2.8, label="12w", fontface=2, size=5)+
    #Arrows
    geom_segment(aes(x=0, xend=0, y=2.1, yend=1.6), arrow = arrow(length=unit(0.25, "cm")), color="black")+
    geom_segment(aes(x=1, xend=1, y=2.1, yend=1.6), arrow = arrow(length=unit(0.25, "cm")), color="black")+
    geom_segment(aes(x=2.5, xend=4.5, y=2.8, yend=2.8), arrow = arrow(length=unit(0.1, "cm")), color="black", size=0.1)+
    geom_segment(aes(x=5.5, xend=11.5, y=2.8, yend=2.8), arrow = arrow(length=unit(0.1, "cm")), color="black", size=0.1)+
    #P-values
      annotate(geom="text", label=paste("p:", toString(format(inflammation_p_values[Week==2, p_value], digits=2, scientific = TRUE)), sep=""), x=2, y=-6.25, fontface=2, size=6, color="red")+
    annotate(geom="text", label=paste("p:", toString(format(inflammation_p_values[Week==5, p_value], digits=2, scientific = TRUE)), sep=""), x=5, y=-6.25, fontface=2, size=6, color="red")+
    annotate(geom="text", label=paste("p:", toString(format(inflammation_p_values[Week==12, p_value], digits=2, scientific = TRUE)), sep=""), x=12, y=-6.25, fontface=2, size=6, color="red")

```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
###################################################################### INDIVIDUAL TARGETS ############################################################
```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
#1. EVALUATING ASSUMPTION OF NORMAL DISTRIBUTION FOR EACH TARGET, TREATMENT AND DAY SEPARATELY (BIOLOGICAL REPLICATES)
norm_function <- function(list_object){
    return(list_object[,p_value:=tryCatch(shapiro.test(list_object[, Expression_normalized])[2], error=function(e){0})])
}
norm_test_p <- do.call(rbind, lapply(split(DT[Sample!="healthy"], DT[Sample!="healthy", .(Sample, Week, Target)]), function(subset){norm_function(subset)}))
norm_test_p <- norm_test_p[, .(p_value = mean(p_value)), by=c("Sample", "Week", "Target")]
norm_test_p <-  rbind(norm_test_p, data.table(Sample="NPC", Week=5, Target="IL1b", p_value=0)) # adding IL1b at 5 weeks for down-stream calculation purposes. 

#2. EVALUATING ASSUMPTION OF HOMOGENITY OF VARIANCES BETWEEN TREATMENTS WITHIN EACH TIME POINT FOR EACH TARGET SEPARATELY
homo_function <- function(list_object){
    return(list_object[,p_value:=tryCatch(fligner.test(list_object$Expression_normalized, factor(list_object$Sample))[3], error=function(e){0})])
}
homo_test_p <- do.call(rbind, lapply(split(DT[Sample!="healthy"], DT[Sample!="healthy", .(Week, Target)]), function(subset){homo_function(subset)}))
homo_test_p <- homo_test_p[, .(p_value=mean(p_value)), by=c("Week", "Target")]

#3. INDEPENDENT INTRA-TIME POINT TWO GROUP COMPARISON 
setkey(homo_test_p, "Week", "Target")
setkey(norm_test_p, "Week", "Target", "Sample")

two_group_test <- function(list_object, norm_values, homo_values){
  week = list_object[, Week][1]
  target = list_object[, Target][1]
  
  norm_assump_1 = FALSE
  norm_assump_2 = FALSE
  homo_assump = FALSE

  #Checking for fulfillment of assumptions
  if(homo_values[.(week, target), p_value]>0.05){
    homo_assump = TRUE
  }
  
  if(norm_values[.(week, target, "NPC"), p_value]>0.05){
    norm_assump_1 = TRUE
  }
  
  if(norm_values[.(week, target, "saline"), p_value]>0.05){
    norm_assump_2 = TRUE
  }
  
  if(isTRUE(norm_assump_1) & isTRUE(norm_assump_2)){
    if(isTRUE(homo_assump)){
      p_value_out <- tryCatch(t.test(list_object[Sample=="saline", Expression_normalized], list_object[Sample=="NPC", Expression_normalized], var.equal = TRUE)$p.value, error=function(e){1})
      return(data.table(Week = week, Target = target, p_value = p_value_out, test = "t.test_equal_var"))
    } else {
      p_value_out <- tryCatch(t.test(list_object[Sample=="saline", Expression_normalized], list_object[Sample=="NPC", Expression_normalized], var.equal = FALSE)$p.value, error=function(e){1})
      return(data.table(Week = week, Target = target, p_value = p_value_out, test = "t.test_unequal_var"))
    }
  } else {
    p_value_out <- tryCatch(wilcox.test(list_object[Sample=="saline", Expression_normalized], list_object[Sample=="NPC", Expression_normalized])$p.value, error=function(e){1})
    return(data.table(Week = week, Target = target, p_value = p_value_out, test = "wilcox_test"))
  }
}

group_comparison_p <- do.call(rbind, lapply(split(DT[Sample!="healthy"], DT[Sample!="healthy", .(Target, Week)]), function(subset){two_group_test(subset, norm_test_p, homo_test_p)}))

```

```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
#1. Summarizing data per target, week and treatment
DT_summary_target <- DT[Sample!="healthy", .(Expression_normalized=mean(Expression_normalized), sd=sd(Expression_normalized), n=.N), by=c("Week", "Target", "Sample")]
DT_summary_target <- DT_summary_target[, SEMx1.96:=qnorm(0.975)*sd/sqrt(n)][, `:=`(CI.lower=Expression_normalized-SEMx1.96, CI.upper=Expression_normalized+SEMx1.96)]

#2. Individual targets plot
individual_target_plot <- function(target){
  p_value_data <- group_comparison_p[Target==target]
  plot_data <- DT[Sample!="healthy" & Target==target]
  plot_data_summary <- DT_summary_target[Target==target]
  
  color_function <- function(week, pos_n){
    p_val <- p_value_data[, p_value][pos_n]
    if(p_val<0.05){out_var="green"} else if (p_val<0.1 & p_val>=0.05){out_var="orange"} else {out_var="red"}
    return(out_var)
    }

  plot_out <- ggplot(plot_data_summary, aes(x=Week, y=Expression_normalized, color=factor(Sample)))+
    geom_segment(aes(x=0, xend=12, y=0, yend=0), color="black", size=1, linetype=2)+
    #Summary data
    geom_errorbar(aes(ymin=CI.lower, ymax=CI.upper), position = position_dodge(width=1), size=3, width=1, show.legend = FALSE, alpha=0.6)+
    geom_point(shape=15, size=4, position = position_dodge(width=1))+
    #Animals
    geom_jitter(plot_data, mapping=aes(x=Week, y=Expression_normalized, color=factor(Sample)), shape=18, size=3, position = position_jitterdodge(jitter.width = 0.5, dodge.width = 1), alpha=0.9)+
    #Legends and shapes    
    xlab("Weeks (Post SCI)")+
    ylab("log2(fold change)")+
    scale_x_continuous(breaks=seq(0,12,1), limits=c(0,13)) +
   scale_y_continuous(breaks=seq(-7, 3, 1), limits = c(-7, 4))+
    theme(axis.title = element_text(size=20, face="bold"), legend.position = "bottom", legend.justification = "center", legend.text = element_text(size=18), legend.title = element_blank(), axis.text = element_text(size=16), axis.line.y = element_blank())+
    scale_color_manual(values=c(brewer.pal(3, "Set1")[1:2], "black"), name="Treatment:", labels=c("SCI+NPC (n=3 or 4/week)", "SCI+Saline (n=3 or 4/week)"))+
    #Annotations
    annotate(geom="text", label="UP-REGULATION", x=6.5, y=4, fontface=2, alpha=0.3, size=6)+
    annotate(geom="text", label="DOWN-REGULATION", x=6.5, y=-7, fontface=2, alpha=0.3, size=6)+
    #Annotations
    annotate(geom="text", label=target, x=6.5, y=2, size=12, fontface=2, alpha=0.8)+
    annotate(geom="text", label=paste("", toString(format(p_value_data[, p_value][1], digits=2, nsmall = 2)), sep = ""), x=2, y=3, fontface=2, size=8, color=color_function(2, 1))+
    annotate(geom="text", label=paste("", toString(format(p_value_data[, p_value][2], digits=2, nsmall = 2)), sep = ""), x=5, y=3, fontface=2, size=8, color=color_function(5, 2))+
    annotate(geom="text", label=paste("", toString(format(p_value_data[, p_value][3], digits=2, nsmall = 2)), sep = ""), x=12, y=3, fontface=2, size=8, color=color_function(12, 3))

  return(plot_out)
}

```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
#HEATMAP AT EACH TIME POINT
DT_heatmap <- DT[Sample!="healthy", .(Expression_normalized=mean(Expression_normalized)), by=c("Week", "Target", "Sample")]
DT_heatmap <- dcast.data.table(DT_heatmap, ...~Target, value.var = "Expression_normalized")
DT_heatmap[Sample=="saline", Sample:="Saline"]

inflammation_heatmap_function <- function(week){
  heatmap_data_raw <- DT_heatmap[Week%in%week]

  col_names <- paste(paste(heatmap_data_raw[,Sample],"\n", heatmap_data_raw[,Week], sep=" "),"w", sep="")
  row_names <- names(heatmap_data_raw[,3:length(heatmap_data_raw)])
  heatmap_data <- heatmap_data_raw[, !c("Sample", "Week")]
  heatmap_data <- round(data.matrix(heatmap_data), digits=1)
  
  heatmap_out <- heatmap.2(heatmap_data,
                           dendrogram="column",
                           trace="none",
                           key=FALSE,
                           
                           cellnote=format(heatmap_data, digits=2), 
                           notecol="black",
                           notecex=5,
                           
                           col=bluered(100),
                           labRow = col_names,
                           cexRow = 4,
                           adjRow = c(0.1,0.5),
                           
                           cexCol = 4,
                           adjCol = c(1,0.5),
                           margins=c(16,10))

  invisible(heatmap_out)  
}

```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
#################################################################### OUTPUT #################################################################################
```

## Pro-inflammation over time

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE, fig.width=14, fig.height=7}
timeoverview_plot
```

**Figure 1.** Figure log2(fold change in expression in relation to mean expresion in healthy control) of pro-inflammatory cytokines/chemokines (GM-CSF, IL12p35, IL1a, IL1b, MIP1a, TNFa) over time for each treatment group. P-values for independent two group comparison is presented at each time point. Color of p-value is green if p-value < 0.05, orange if p-value > 0.05 & p-value < 0.1 and red if p-value >0.1. Test is selected based on evaluation of assumptions.    

## Individual cytokines/chemokines over time

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE, fig.width=20, fig.height=10}
plot_grid(individual_target_plot("GM-CSF"), individual_target_plot("IL12p35"), individual_target_plot("IL1a"), individual_target_plot("IL1b"))

```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE, fig.width=20, fig.height=5}
plot_grid(individual_target_plot("MIP1a"), individual_target_plot("TNFa"))

```

**Figure 2:** Each plot reports log2(fold change in expression in relation to mean expresion in healthy control) of one cytokine. P-values for comparison of the two independent groups are presented at each time point. Color of p-value is green if p-value < 0.05, orange if p-value > 0.05 & p-value <  and red if p-value > 0.1. 

## Heatmap 2 weeks post SCI

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE, fig.width=20, fig.height=10}
inflammation_heatmap_function(2)

```

## Heatmap 5 weeks post SCI

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE, fig.width=20, fig.height=10}
inflammation_heatmap_function(5)

```

## Heatmap 12 weeks post SCI

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE, fig.width=20, fig.height=10}
inflammation_heatmap_function(12)

```

## Heatmap 2, 5 and 12 weeks post SCI

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE, fig.width=20, fig.height=20}
inflammation_heatmap_function(c(2,5,12))

```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
#P-VALUES FOR DIFFERENCE IN PRO-INFLAMMATION BETWEEN TREATMENTS WITHIN WEEK
kable(cbind(inflammation_p_values[,1], round(inflammation_p_values[,2], 3)), align="c", col.names = c("Week", "P-value"))

```

**Table 1.** P-values for comparison of pro-inflammation between treatments within week.

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
#P-VALUES FOR DIFFERENCE IN PRO-INFLAMMATION WITHIN TREATMENTS BETWEEN WEEK
kable(cbind(overtime_comparison_p[,1], round(overtime_comparison_p[,2],3)), align="c", col.names = c("Treatment", "P-value"))

```

**Table 2.** P-values for comparison of pro-inflammation within treatment between weeks. 

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
p_value_data <- group_comparison_p[,1:3] 
p_value_data <- dcast.data.table(p_value_data, Target~Week, value.var = "p_value")
kable(cbind(p_value_data[,1], round(p_value_data[, 2:4],3)), align="c")

```

**Table 3.** P-values for difference in expression of cytokine/chemokine between treatments within week.

\newpage

```{r echo=TRUE, error=FALSE, warning=FALSE, message=FALSE}
sessionInfo()

```

```{r echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
#SAVING PLOTS
#1. Inflammation over time
#ggsave("NPC_PCR_overtime.jpeg", timeoverview_plot, dpi=1000, width=14, height=7)

# #2. Heatmap at 2 weeks
# jpeg('heatmap_2w.jpg',
#      width=3000,
#      height=1000,
#      quality=100)
# inflammation_heatmap_function(2)
# dev.off()

# #3. Individual cytokines
# ggsave("MIP1a.jpeg", individual_target_plot("MIP1a"), dpi=1000, width=14, height=7)
# ggsave("TNFa.jpeg", individual_target_plot("TNFa"), dpi=1000, width=14, height=7)
# ggsave("GM-CSF.jpeg", individual_target_plot("GM-CSF"), dpi=1000, width=14, height=7)
# ggsave("IL12p35.jpeg", individual_target_plot("IL12p35"), dpi=1000, width=14, height=7)
# ggsave("IL1a.jpeg", individual_target_plot("IL1a"), dpi=1000, width=14, height=7)
# ggsave("IL1b.jpeg", individual_target_plot("IL1b"), dpi=1000, width=14, height=7)

```





